---
title: "&nbsp;"
output:
  html_document:
    css: [./css/Publications.css, ./css/navbar.css, ./css/body.css]
    includes:
      in_header: ./heros/Publications_hero.html
---

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE} 
library(fontawesome)
```

<link rel="stylesheet" href="https://cdn.jsdelivr.net/gh/jpswalsh/academicons@1/css/academicons.min.css">

<style>
.Section_link{
  background-color: #4CAF50;
  border: none;
  border-radius: 15px;
  color: black;
  text-align: center;
  text-decoration: none;
  display: inline-block;
  font-size: 20px;
  width: 180px;
  height: 50px;
  line-height: 2em;
  margin-right: 5%;
  margin-left: 5%;
  font-family: "Open Sans";
}

h1 {text-align: center !important; 
   font-weight: bold !important; 
   font-size: 42px !important}
   
:target {
    display: block;    
    position: relative;     
    top: -150px;
    visibility: hidden;
}
</style>

<div style="text-align: center">
  <a class="Section_link btn btn-primary btn-outline btn-xs" href="#Journal Articles">
    Journal Articles
  </a>
    <a class="Section_link btn btn-primary btn-outline btn-xs" href="#R Packages">
    R Packages
  </a>
    <a class="Section_link btn btn-primary btn-outline btn-xs" href="#Others">
    Others
  </a>
</div>

<br>

<div style="font-size: 100px; text-align: center">
<a href="https://orcid.org/0000-0002-6607-4382" style="color: #A6CE39; margin-right: 2.5%; margin-left: 2.5%;"><i class="ai ai-orcid ai"></i></a>
<a href=# style="color: black; margin-right: 2.5%; margin-left: 2.5%;"><i class="ai ai-google-scholar ai"></i></a>
</div>

<br>
<br>
<a id="Journal Articles">
</a>

# Journal Articles
<br>

## 2021
<br>
<br>
<br>
<br>
<br>
<br>


<a id="R Packages"> </a>

# R Packages
<br>
<br>
<br>
<br>
<br>
<br>


<a id="Others"> </a>

# Others
<br>
<br>
<br>
<br>
<br>
<br>

```{r showChoro1, echo=FALSE}
htmltools::includeHTML("")
```

<div class="pub-list-item" style="margin-bottom: 1rem" itemscope itemtype="http://schema.org/CreativeWork">
  <i class="fa fa-file-text-o pub-icon" aria-hidden="true"></i>
  <span itemprop="author">
    <strong style="text-decoration: underline">Bimler, M.D.</strong>, Ross Cunning, Rachael A. Bay, Andrew C. Baker, Nikki Traylor-Knowles</span>
  (2018).
  <a href="https://baylab.github.io/publication/2018_cunning_et_al_scientific_reports/" itemprop="name">Comparative analysis of the Pocillopora damicornis genome highlights role of immune system in coral evolution</a>.
  <em>Scientific Reports</em>.
  
  <p>
<a class="btn btn-primary btn-outline btn-xs" href="https://baylab.github.io/pdf/2018_Cunning_et_al_Scientific_Reports.pdf" target="_blank" rel="noopener">
  PDF
</a>
</p>

</div>





